% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Scholarships and additional info
\sectionTitle{Research Interest and Publications}{\faQuoteRight}

\textbf{{Research Interest}}
\begin{enumerate}
	\item Image \& Video Compression Techniques for Medical Applications.
	\item Biomedical Signal Processing.
	\item Cellular \& Wireless communication.
\end{enumerate}
	\textbf{{International Journal}}
\begin{enumerate}
	

	\item Objective analysis of HEVC (h.265) compressed FMRI Images, International Journal of Control Theory \& Application,Volume 9, number 41, pp.199-206, 2017, ISSN:0974-5572. \textbf{(Scopus Indexed Journal)}
	
	\item A Hybrid connecting character based text recognition and extraction algorithm, International Journal of Recent and Innovation Trends in Computing and Communication, Volume 6, Issue 6, pp 102-105, ISSN:2321-8169.
	
	\item Dual Band ‘I’ Shaped MSA with Diffracted
	Ground Plane, International Journal of Innovative Research in Computer and Communication Engineering, Volume 5, Issue 6, pp 12253-12260, ISSN(Online): 2320-9801,ISSN (Print): 2320-9798.
	
	\item BER Analysis of MIMO OFDM System in AWGN \& Rayleigh Fading Channel”, International Journal of Computer Application (IJCA), Volume 34, Issue 9, November 2011, ISSN: 0975-8887.
		
	\item Evaluating the Impact of Guard Period Insertion on the Performance of MIMO OFDM System, International Journal of Engineering Research \& Applications (IJERA) Volume 1, Issue 4, November 2011, ISSN: 2248-9622.
	
	\item Effect of Guard Period Insertion in MIMO OFDM System, International Journal of Computer Technology and Electronics Engineering (IJCTEE) Volume 1, Issue 2, November 2011, ISSN: 2249-6343.
	\item Review of Congestion Control Algorithms for Performance Evaluation of WCDMA, International Journal of Emerging Technology and Advanced Engineering (IJETAE) , Volume 1, Issue 1, November 2011, ISSN 2250-2459.
	
	\item The System Design And Modelling Using Mix-Signal \& Mix-Technology, with VHDL-AMS, International Journal of Electronic, Electrical and Communication Engineer (IJEECE), Vol.3, No.2, 2011,ISSN: 0975-4814.
	
	\item Performance of Turbo Code for UMTS in AWGN channel, International Journal of Advanced ComputerResearch (IJACR), Vol.1, No.1 September 2011, ISSN: 2249-7277.
	
	\item Speed-Improvement of Fractal Image Encoding, International Journal of Computer System Engineering and 
	Information Technology, vol. 3, no. 1, January-June 2010, ISSN: 0974-5807.
	
	\item Effect of Different Spreading Codes on DS-CDMA System in Multipath Fading, International Journal of ELECTRONICS AND COMPUTERS, Volume 2, number1, pp.65-71,January-June 2010, ISSN:0975-3796.
	
\end{enumerate}
\textbf{{International Conferences}}
\begin{enumerate}
	\item Quality Evaluation of HEVC Compressed CT Images, IEEE UPCON-2015, IEEE UP Section Conference on Electrical, Computer and Electronics (4-6 December, 2015), Indian Institute of Information Technology Allahabad - 211012, India.
	
	\item Taxonomy of Brain Imaging Techniques, ICIREMPS 2K14, (IEEE MP Subsection) Bhopal, India, pp 1098-1101.
	
	\item Performance of Turbo Code Using SOVA Decoder in AWGN channel, ICEICE – 2010 Coimbatore, India.
	
	\item Speed-Improvement of Fractal Image Encoding, International conference on Trends \& Advances in Computation and Engineering (TRACE-2010) Bhopal, (India).
	
	\item Different Spreading Codes on DS-CDMA System in Multipath Fading”, International Conference of Emerging Trends In Engineering And Technology, First impression: 2010, pp. 613- 616, ISBN: 978- 93-80697-22-2. Oct 14-16-2010, Nagpur (India).
	
\end{enumerate}

\textbf{{National Conferences}}
\begin{enumerate}
	\item A Study of Mobility Aware Sensor-MAC Protocol for Wireless Sensor Networks”, National Conference on VLSI Embedded Systems, Signal Processing and Communication Technologies, Bhopal (India), March 2010.
	
	\item Energy Technologies for the 21st Century- The role of Renewable energy, National Conference on Efficient conversion of new \& Renewable Energy for Electricity and Fuel, Bhopal (India), 22-23 December 2008.
	
	\item The System Design and Modeling Using Mix-Signal \& Mix-Technology, with VHDL-AMS”, Recent Trends in Signal Processing \& Design, GGITM Bhopal with IEEE M.P. Subsection, 18 Nov to 20 Nov. 2011.

\end{enumerate}