% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Scholarships and additional info
\sectionTitle{Membership, Professional affiliation \& Activities}{\faMortarBoard}

\begin{enumerate}
	

	\item Associate Member of UACEE (Universal Associate of Computer \& Electronics Engineers) International Association of Engineers) California (CA 93105), USA, Membership No.: AM1004291.
	
	\item Member of IAENG (The International Association of Engineers) Hong Kong, Membership No.132472.
	
	\item Editorial Board Member for International Journal of Electronics Communication and Computer Engineering(IJECCE), ISSN : 2249-071X.
	
	\item Reviewer Board Member for International Journal of Image Processing (IJIP), CSC Journals, Kuala Lumpur, Malaysia, ISSN (Online)- 1985-2304.
	
	\item Reviewer Board Member for International Journal of Engineering Research \& Applications (IJERA), ISSN: 2248-.9622.
	
	\item Editor Board Member for IJTRA (International Journal of Technical Research and application), ISSN No.:2321-7322 (Print).
	
	\item Editor Board Member for IJAIM (International Journal of Artificial Intelligence and Mechatronics), ISSN No.:2320-5121 (Print).
	
	\item Editor Board Member for IJEST (International Journal of Engineering Science \& Technology), ISSN No.:2278-9510 (Print).
	
	\item Editor Board Member for IJACR (International Journal of Advanced Computer Research),ISSN: (Print): 2249-7277,ISSN: (Online):2277–7970.
	
	\item Mission10X Learning approach (MxLA) practitioner.
	
	\item Wipro certified Teacher \& Trainer.
	\item MATLAB Trainer.

\end{enumerate}

