% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Till date}   {T\&P Coordinator (OGI)| Associate Professor,
    	 Department of ECE}{Oriental College of Technology, Bhopal}{India}
    {August 2016} {\textbf{As Associate Professor}\\
    				\textit{Teaching}
                      \begin{itemize}
                        \item Designing and developing innovative approaches to the learning experience for undergraduates and postgraduates with the intention of challenging thinking, fostering debate, and encouraging the development of intellectual reasoning and rigour.                       
                        \item Delivering teaching to the undergraduate students with multiple teaching aid for their better understanding of the subject.                 
                        \item Preparing and circulating of the E-notes for their quick revision.                  
                        \item Conduction of test, quizzers, mid semester examination, viva-voce and assignemnts to fulfillment the university academics requirements.                                                                   
                      \end{itemize}
                
                  		\textit{Administration}
                  		\begin{itemize}
                  			
                  			\item Participates in relevant committees within department/faculty.  
                  			
                   			\item Providing Letter of reference to the students.        
                  			               
                  			\item Mentoring the new faculty member as of required.
                  			
                  			\item Member of NBA accreditation preparation team for required documentation.     
                  			         
                  			\item May, on occasion, participate in school/University committees where appropriate and/or where invited.  
                  	    \end{itemize}
                     
                      \textit{Research}
                      \begin{itemize}
                      
                      	\item Investigating new areas of research within specialist subject area. 
                      	\item Identifying research topic and initiating analysis that will be original and innovative for PG scholars.
                     	\item Adapting research methodologies and its implementation.
                      	  
                      \end{itemize}
                         \vspace{0.5em}
	                  \textit{Training \& Placement}
                  	\begin{itemize}
                  	
                  	\item Correspond to prospective companies for interview date and schedule of events
                  	\item Registration of students in training and placement and various assessment test conduction
                  	\item Arrange for interview facilities at the campus and written test halls
                  	\item Receiving the personnel and providing necessary inputs about the college for smooth functioning at various locations (interview halls, written test halls, canteen, etc.)
                  	\item Contacting the HR’s of various organizations for campus drives and accreditation process
                  	\item Placement drive conduction
                  	\item Conduction of GD PI and Technical interviews (Mock)
                  	\item Setting recruitment schedule, and feedback of trainers
                  	\item Distribution of appointment letters and collection of acceptance letters from the students to dispatch the same to the employees
                  	\item VAC schedule, training forms, industrial training arrangements.
                  	
                  \end{itemize}
                    }
                    {Administration,Training,TPO,MATLAB,ERP,Multisim,Kicad }
  \emptySeparator
  \experience
    {August 2016} {Head, ECE | Associate Professor | TPO}{SIRT-Excellence, Bhopal}{INDIA}
    {January 2012}    {
                     	\textit{Administration as Head of the Dept.}
                     \begin{itemize}
                     	\item Arranging various workshop, expert lectures, industrial visits and value addition courses for filling the universty academics curriculum and industrial requirement from the students.
                     	
                     	\item Participates in relevant committees within Institute or group level.  
                     	
                     	\item Subject Secretary of Dept of EC within group level.        
                     	
                     	\item Member of documentation team for AICTE, RGPV, NBA and ISO compliance team.
                     	
                     	\item Member Research \& development team within group level.     
                     	
                     	\item May, on occasion, participate in school/University committees where appropriate and/or where invited.  
                     \end{itemize}
                     \textit{Training \& Placement}, \textit{Teaching} and \textit{Research }as above.
                    }
                    {R\& D, ERP, MATLAB, Workshop,FDP,Administration, TPO}
  \emptySeparator
  \experience
    {December 2011}     {HOD,EC | Reader}{NRI Group of Institution, Bhopal}{INDIA}
    {October 2008}    {
                      \begin{itemize}
                        \item Duties \& responsibilities as Head of the department.
                        \item Development \& Management of laboratory of 60 computers.
                        \item Internet management \& maintenance monitoring.
                        \item Teaching \& Development of Electronics Lab.
                        \item Co-ordinator for e-learning \& cultural events.
                        \item Member for faculty recruitment cell.
                        \item M.Tech Thesis Guide.
                        \item Teaching \& development of Advance Communication Laboratory.
                        
                      \end{itemize}
                  \textit{Teaching} and \textit{Research}as above.
                    }
                    {Administration,R\&D,MATLAB,NBA,ISO,MxLA,WCTT}

  \emptySeparator
 
  
  \experience
  {October 2008}  {Assistant Professor}{All Saints' College of Technology, Bhopal}{INDIA}
  {February 2006}   {
                      
                      \begin{itemize}
                       \item Teaching \& Development of Microprocessor and VLSI Lab
                       Coordinated 3 Technical Symposium Techno vista 2006, 2007 and Vision Tech -2008
                       \item Coordinator of Cultural events
                        
                      \end{itemize}
                  }
                  {Management,Administration,R\&D,MATLAB,NBA,ISO,VLSI} 
 \emptySeparator
 
 
 \experience
 {May 2005}  {Lecturer}{Oriental Institute of Science \& Technology, Bhopal}{INDIA}
 {January 2005}   {
 	
 	\begin{itemize}
 		\item Manufacturing \& Maintenance of Micro-controller based Systems(Atmel 89C5X based).
 		
 		
 	\end{itemize}
 }
 {Assembly language,Maintenance,AVR,Embedded system,ISO} 
                  
 \emptySeparator


\experience
{August 2003}  {Maintenance Engineer}{Microcoms Communication System, Bangalore}{INDIA}
{August 2001}   {
	
	\begin{itemize}
		\item Manufacturing \& Maintenance of Micro-controller based Systems(Atmel 89C5X based).
		
		
	\end{itemize}
}
{Assembly language,Maintenance,AVR,Embedded system,ISO} 
\end{experiences}
